Análisis de datos

### 2023-10-30 procesamiento/prod_analysis-non-confusian-sample.Rmd
lunes

>>>>

# Numeric -  Egalitarian Attitudes Index

Cronbach's alpha is 0.7 for:

1. It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes. 
2. For a society to be fair, differences in people's standard of living should be small.

Note: the item "Differences in income in [COUNTRY] are too large" is not included because of two reasons. First, the item is fuzzy in terms of what is it measuring, "are" refers to a perception about inequality and "too large" as a normative judgement. Second, the literature has addressed this indicator as perceived or concerns about inequality.

<!----------------------------------------------------------------------------->

```{r mod-homclass-numeric,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(
                        egal=egal2,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
  na.omit()

# Models 
base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
knitreg(models)
save(models,file = here::here("output/nonconfusian-egalitarian-homclass-full-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(egal=egal2,
                               class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
# summary(giniD_int)

giniM_gdp<- update(base, . ~ . +gini_mkt+logrgdpna)
giniM_rs <- update(giniM_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniM_gdp,giniM_rs)
giniM_int <- update(giniM_rs, . ~ . + homclass*gini_mkt + (homclass|country2))
# summary(giniM_int)
models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-egalitarian-homclass-full-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-egalitarian-homclass-full-individual.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-egalitarian-homclass-full-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

```{r mod-homclass-numeric-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(egal=egal2,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%  
  na.omit()

# Models 
base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-egalitarian-homclass-strong-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(egal=egal2,
                        class3,
                        homclass=homclass_s,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-egalitarian-homclass-strong-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-egalitarian-homclass-strong-individual.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-egalitarian-homclass-strong-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

```{r mod-homclass-numeric-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(egal=egal2,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
  na.omit()

# Models 
base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-egalitarian-homclass-weak-individual.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric-strong-ties,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(egal=egal2,
                        class3,
                        homclass=homclass_w,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
filter(!country2 %in% c("TWN","CHN","JPN","SLV")) %>%
  na.omit()

# Homoclass x Gini--------------------------------------------------------------
main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-egalitarian-homclass-weak-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-egalitarian-homclass-weak-individual.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-egalitarian-homclass-weak-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```
## R's class

```{r mod-homclass-numeric-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(egal=egal2,
                        class3=class3res,
                        homclass=homclass_res,
                        class3spo,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN","SLV"))

# Models 
base <- lmer(egal~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + class3+female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst+class3spo)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,full1,rob1,int_homo)
save(models,file = here::here("output/nonconfusian-egalitarian-homclass-respondent.RData"),compress = "gzip")
```

```{r mod-intermacro-numeric-respondent,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(egal=egal2,
                        class3=class3res,
                        class3spo,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country,
                        palmaratio,
                        top10,
                        middle50,
                        d10d1,
                        giniindex,
                        ttheilge1
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  filter(!country2 %in% c("TWN","CHN","JPN","SLV"))

# Homoclass x Gini--------------------------------------------------------------
main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+class3spo+(1|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
giniD_gdp<- update(base, . ~ . +gini_disp+logrgdpna)
giniD_rs <- update(giniD_gdp, . ~ . - (1|country2) + (homclass|country2))
# anova(giniD_gdp,giniD_rs)
giniD_int<- update(giniD_rs, . ~ . + homclass*gini_disp + (homclass|country2))
summary(giniD_int)

# Homoclass x Other Economic Inequality-----------------------------------------
main <- "egal~class3+homclass+edyears+Q03pcm+workst+union+female+agenum+age2+logrgdpna+class3spo+(homclass|country2)"
base <- lmer(formula(main),data=dfreg,weights = WEIGHT)
int_palma <- update(base, . ~ . +homclass*palmaratio)
int_pc10  <- update(base, . ~ . +homclass*top10)
int_pc50  <- update(base, . ~ . +homclass*middle50)
int_d10d1 <- update(base, . ~ . +homclass*d10d1)
int_gini_wiid <- update(base, . ~ . +homclass*giniindex)
int_theil  <- update(base, . ~ . +homclass*ttheilge1)

models_m <- list(int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil
                 )
save(giniD_gdp,giniD_rs,giniD_int,
                 giniM_gdp,giniM_rs,giniM_int,
                 int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil,
     file = here::here("output/nonconfusian-egalitarian-homclass-respondent-macro.RData"),compress = "gzip")
```

```{r}
load(here::here("output/nonconfusian-egalitarian-homclass-respondent.RData"))
texreg::knitreg(models)

load(here::here("output/nonconfusian-egalitarian-homclass-respondent-macro.RData"))
texreg::knitreg(list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,
                 int_gini_wiid,int_theil))
```

### 2023-10-30 procesamiento/prod_analysis-tables-macro.Rmd
lunes

@@

@@

>>>>

load(here::here("output/fullsample-egalitarian-homclass-full-macro.RData"));fsample_egal_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/fullsample-egalitarian-homclass-strong-macro.RData"));fsample_egal_strong_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/fullsample-egalitarian-homclass-weak-macro.RData")); fsample_egal_weak_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)

htmlreg(
  c(fsample_egal_full_mac,fsample_egal_strong_mac,fsample_egal_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

@@

```{r nonconfusian-lmer-egalitarian-macro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())
coef_map <-
  list(
    homclass = "Homogeneity",
    logrgdpna = "log GDP",
    "gini_disp" = "GiniD ",
    "homclass:gini_disp" = "Hom:Gini(D)",
    "gini_mkt" = "Gini(M) ",
    "homclass:gini_mkt" = "Hom:Gini(M)",
    palmaratio               = "Palma",
    "homclass:palmawd"      = "Hom:Palma",
    top10             = "Top 10%",
    "homclass:top10"    = "Hom:top10",
    middle50             = "Bott.50%",
    "homclass:middle50"    = "Hom:bott50",
    d10d1             = "D10/D01",
    "homclass:d10d1"    = "Hom:D10D01",
    giniindex             = "Gini(WIID)",
    "homclass:giniindex"    = "Hom:Gini(WD)",
    ttheilge1             = "Theil",
    "homclass:ttheilge1"    = "Hom:Theil"
  )

load(here::here("output/nonconfusian-egalitarian-homclass-full-macro.RData"));nconf_num_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/nonconfusian-egalitarian-homclass-strong-macro.RData"));nconf_num_strong_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/nonconfusian-egalitarian-homclass-weak-macro.RData")); nconf_num_weak_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)

htmlreg(
  c(nconf_num_full_mac,nconf_num_strong_mac,nconf_num_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

@@

```{r ocde-lmer-egalitarian-macro,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())
coef_map <-
  list(
    homclass = "Homogeneity",
    logrgdpna = "log GDP",
    "gini_disp" = "GiniD ",
    "homclass:gini_disp" = "Hom:Gini(D)",
    "gini_mkt" = "Gini(M) ",
    "homclass:gini_mkt" = "Hom:Gini(M)",
    palmaratio               = "Palma",
    "homclass:palmawd"      = "Hom:Palma",
    top10             = "Top 10%",
    "homclass:top10"    = "Hom:top10",
    middle50             = "Bott.50%",
    "homclass:middle50"    = "Hom:bott50",
    d10d1             = "D10/D01",
    "homclass:d10d1"    = "Hom:D10D01",
    giniindex             = "Gini(WIID)",
    "homclass:giniindex"    = "Hom:Gini(WD)",
    ttheilge1             = "Theil",
    "homclass:ttheilge1"    = "Hom:Theil"
  )

load(here::here("output/ocde-egalitarian-homclass-full-macro.RData"));ocde_num_full_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/ocde-egalitarian-homclass-strong-macro.RData"));ocde_num_strong_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)
load(here::here("output/ocde-egalitarian-homclass-weak-macro.RData")); ocde_num_weak_mac<- list(giniD_int,giniM_int,int_palma,int_pc10,int_pc50,int_d10d1,int_gini_wiid,int_theil)

htmlreg(
  c(ocde_num_full_mac,ocde_num_strong_mac,ocde_num_weak_mac),
  caption = "Multilevel linear regression: full country sample cross-level interaction - egalitarian index",
  caption.above = T,
  custom.coef.map= coef_map,
  custom.header = 
    list(
      "Full network"=1:8,
      "Strong ties"=9:16,
      "Weak ties"=17:24
      ))
```

### 2023-10-30 procesamiento/prod_analysis-tables-micro.Rmd
lunes

@@

@@

>>>>

```{r full-lmer-micro-egalitarian,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())

load(here::here("output/fullsample-egalitarian-homclass-full-individual.RData")); fsample_num_full_ind<- models
load(here::here("output/fullsample-egalitarian-homclass-strong-individual.RData"));fsample_num_strong_ind<- models
load(here::here("output/fullsample-egalitarian-homclass-weak-individual.RData")); fsample_num_weak_ind<- models

htmlreg(
  c(fsample_num_full_ind,fsample_num_strong_ind,fsample_num_weak_ind),
  caption = "Multilevel linear regression: full country sample - egalitarian preferences index",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

@@

```{r nonconfusian-lmer-micro-egalitarian,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())

load(here::here("output/nonconfusian-egalitarian-homclass-full-individual.RData")); fsample_num_full_ind<- models
load(here::here("output/nonconfusian-egalitarian-homclass-strong-individual.RData"));fsample_num_strong_ind<- models
load(here::here("output/nonconfusian-egalitarian-homclass-weak-individual.RData")); fsample_num_weak_ind<- models

knitreg(
  c(fsample_num_full_ind,fsample_num_strong_ind,fsample_num_weak_ind),
  caption = "Multilevel linear regression: Non-confusian sample - egalitarian preferences index",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

@@

```{r oecd-lmer-micro-egalitarian,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,texreg)  
rm(list=ls())

load(here::here("output/ocde-egalitarian-homclass-full-individual.RData")); fsample_num_full_ind<- models
load(here::here("output/ocde-egalitarian-homclass-strong-individual.RData"));fsample_num_strong_ind<- models
load(here::here("output/ocde-egalitarian-homclass-weak-individual.RData")); fsample_num_weak_ind<- models

knitreg(
  c(fsample_num_full_ind,fsample_num_strong_ind,fsample_num_weak_ind),
  caption = "Multilevel linear regression: OECD country sample - egalitarian preferences index",
  caption.above = T,
  custom.header = 
    list(
      "Full network"=1:4,
      "Strong ties"=5:8,
      "Weak ties"=9:12
      ))
```

### 2023-10-30 procesamiento/prod_analysis.Rmd
lunes

>>>>

# Check on homogeneity

```{r}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,haven,sjmisc,GGally,ggplot2)
load(here::here("input/data/proc/study1_country.RData"))

test <- df2
frq(df2$class11d)
test$egp3_v1 <- car::recode(test$class11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))
test$egp3_v2 <- car::recode(test$digclass11d,"1:2=1;c(3,4,5,6)=2;7:10=3",as.factor = T,levels = c(1,2,3))

# I   II IIIa IIIb  IVa  IVb  IVc    V   VI VIIa VIIb 
#   1    2    3    4    5    6    7    8    9   10   11 
frq(df2$dclass11d)
test$egp3_v3 <- car::recode(test$dclass11d,"1:2=1;c(3,4,5,6,7,8)=2;9:11=3",as.factor = T,levels = c(1,2,3))
test$egp3_v4 <- car::recode(test$dclass11d,"1:2=1;c(3,5,6,7,8)=2;c(4,9,10,11)=3",as.factor = T,levels = c(1,2,3))

# Service class II to middle class
test$egp3_v5 <- car::recode(test$dclass11d,"1=1;c(2,3,5,6,7,8)=2;c(4,9,10,11)=3",as.factor = T,levels = c(1,2,3))

frq(test$egp3_v1)
frq(test$egp3_v2)
frq(test$egp3_v3)
frq(test$egp3_v4)
frq(test$egp3_v5)
frq(test$class3)

test$ingroup1 <- NA 
test$ingroup1 <- ifelse(test$egp3_v1==1,test$n_high,test$ingroup1)
test$ingroup1 <- ifelse(test$egp3_v1==2,test$n_middle,test$ingroup1)
test$ingroup1 <- ifelse(test$egp3_v1==3,test$n_low,test$ingroup1)

test$ingroup2 <- NA 
test$ingroup2 <- ifelse(test$egp3_v2==1,test$n_high,test$ingroup2)
test$ingroup2 <- ifelse(test$egp3_v2==2,test$n_middle,test$ingroup2)
test$ingroup2 <- ifelse(test$egp3_v2==3,test$n_low,test$ingroup2)

test$ingroup3 <- NA 
test$ingroup3 <- ifelse(test$egp3_v3==1,test$n_high,test$ingroup3)
test$ingroup3 <- ifelse(test$egp3_v3==2,test$n_middle,test$ingroup3)
test$ingroup3 <- ifelse(test$egp3_v3==3,test$n_low,test$ingroup3)

#ingroup with Routine non-manual IIIa as middle class and IIIb as working class
test$ingroup4 <- NA 
test$ingroup4 <- ifelse(test$egp3_v4==1,test$n_high,test$ingroup4)
test$ingroup4 <- ifelse(test$egp3_v4==2,test$n_middle,test$ingroup4)
test$ingroup4 <- ifelse(test$egp3_v4==3,test$n_low,test$ingroup4)

#ingroup with Service II + Routine non-manual IIIa as middle class and IIIb as working class
test$ingroup5 <- NA 
test$ingroup5 <- ifelse(test$egp3_v5==1,test$n_high,test$ingroup4)
test$ingroup5 <- ifelse(test$egp3_v5==2,test$n_middle,test$ingroup4)
test$ingroup5 <- ifelse(test$egp3_v5==3,test$n_low,test$ingroup4)

test$homclass_v1 <- as.numeric(test$ingroup1/test$know_total)
test$homclass_v2 <- as.numeric(test$ingroup2/test$know_total)
test$homclass_v3 <- as.numeric(test$ingroup3/test$know_total)
test$homclass_v4 <- as.numeric(test$ingroup4/test$know_total)
test$homclass_v5 <- as.numeric(test$ingroup5/test$know_total)

sjPlot::plot_frq(test$homclass_v1,type = "bar")
sjPlot::plot_frq(test$homclass_v2)
sjPlot::plot_frq(test$homclass_v3,type = "bar")
sjPlot::plot_frq(test$homclass_v4,type = "bar")
sjPlot::plot_frq(test$homclass_v5,type = "bar")

hist.default(df2$homclass)
```

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,marginaleffects,sjlabelled,haven,stringr,ordinal,texreg)  
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- test %>% dplyr::select(redist,
                        class3,
                        homclass,
                        Q03pcm,
                        edyears,
                        female,
                        agenum,
                        union,
                        workst,
                        WEIGHT,
                        region,
                        "gini_disp",
                        "gini_mkt",
                        rgdpna,
                        oecd,
                        country2,country
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         edyears2=edyears^2,
         age2=agenum^2) %>%
  na.omit()

hist.default(dfreg$homclass,main = "Class-based network homogeneity",xlab = NULL)

# Models 
base <- lmer(redist~1 + (1|country2),data=dfreg,weights = WEIGHT); icc1<- performance::icc(base)
homclass<- update(base, . ~ . +homclass)
full1 <- update(homclass, . ~ . + female+agenum+age2)
rob1 <- update(full1, . ~ . + class3+edyears+ Q03pcm+union+workst)
rob2 <- update(rob1, . ~ . -(1|country2) + (homclass|country2))
# anova(rob1,rob2)
# Interactions segregation x class
int_homo <- update(rob1, . ~ . +class3*homclass)

models <- list(homclass,rob1,int_homo)

knitreg(list(homclass,full1,rob1,int_homo))
```
